SciUnit: Collaborative Infrastructure for Test-Driven\\Scientific Model Validation

### 2014-03-13 sciunit-icse14/sciunit-icse14.tex

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{SciUnit: Collaborative Infrastructure for Test-Driven\\Scientific Model Validation}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations
\numberofauthors{2}
\author{\alignauthor
Cyrus Omar, Jonathan Aldrich\\\affaddr{Carnegie Mellon University}\\
       \email{\{comar,aldrich\}@cs.cmu.edu}
       \alignauthor Richard C. Gerkin\\
       \affaddr{Arizona State University}\\{rgerkin@asu.edu}
}

>>>>

\usepackage{enumitem}
\setenumerate{noitemsep,topsep=2pt,parsep=0pt,partopsep=0pt}
\newcommand{\subparagraph}{}
\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{*0}{*0}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}

\begin{document}
\conferenceinfo{ICSE}{'14, May 31 - June 7, 2014, Hyderabad, India}
\CopyrightYear{2014}
\crdata{978-1-4503-2768-8/14/05}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{SciUnit: Collaborative Infrastructure for Test-Driven\\Scientific Model Validation}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations
\numberofauthors{2}
\author{\alignauthor
Cyrus Omar, Jonathan Aldrich\\\affaddr{Carnegie Mellon University, USA}\\
       {\{comar,aldrich\}@cs.cmu.edu}
       \alignauthor Richard C. Gerkin\\
       \affaddr{Arizona State University, USA}\\{rgerkin@asu.edu}
}
